Untitled

### 2018-08-10 MSOAmodel.Rmd
Subset Bootstrapping
The previous bootstrap functions didn't have the LowUse homes as a subset of the regular homes. I have now chnaged the Strapped functions so that this is the case. Previously this meant that the LowUse and Homes were actually independent, this caused side effects especially on smaller geographys

@@

AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 501)

test <- LSOAPriceList %>% map_int(length(.x))

>>>>

#Calc Real Quantiles for all data

This takes ages and gives an almost identical number to simple running quantiles on the whole dataset

```{r Real Quantile Chunk}

@@

AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 501)
setwd(basewd)

saveRDS(AllDataQuartiles, "AllDataQuartiles.rds")

test <-  AllDataQuartiles %>%
   select(-X0.,-X100.) %>%
   summarise_all(funs(mean, sd)) %>%
   mutate(X25Perc = X25._sd/X25._mean,
          X50Perc = X50._sd/X50._mean,
          X75Perc = X75._sd/X75._mean)

prices %>%
   filter(X5 %in% c("D", "S", "T", "F")) %>%
  pull(X2) %>% quantile()

### 2018-08-10 PaperCode.Rmd
Subset Bootstrapping
The previous bootstrap functions didn't have the LowUse homes as a subset of the regular homes. I have now chnaged the Strapped functions so that this is the case. Previously this meant that the LowUse and Homes were actually independent, this caused side effects especially on smaller geographys

@@

@@

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapQuartiles")
BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501)
BootStrapRes <- LoadBootstrapData()

@@

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501, GroupingVars = "MSOA11CD")

#Temporay untill the proper one is complete
setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
BootStrapRes <- LoadBootstrapData()

@@

```{r}
CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
  df %>% 
  group_by(ID, class) %>%
  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
  group_by(ID)%>%
  mutate(RatioExvsAct = LowUse/sum(LowUse)) %>%
  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1)
}

@@

CleanForPlotClassDiff(BootStrapRES$ChelseaLON)  %>%
PlotClassDiff(., "Kensington and Chelsea")
SaveFig("ClassdiffChelsea.pdf")

@@

#Plot for all data
All_data_class <- BootStrapRES %>% 
  bind_rows %>%
  select(CountryClass, ID, LowUse, Homes) %>%
  rename(class = CountryClass)%>%
  CleanForPlotClassDiff

>>>>

#This is no longer needed
rm(PstCdLSOA.raw)

@@

#Calculate Quantiles

 This is not the right way to do it but give almost identical values to the weighted sampled quantiles. 
 if you don't believe me see "MSOAmodel.Rmd" section "Calc Real Quantiles for all data". It takes ages and you regret everything

 PropertyTypes <- c("D", "S", "T", "F")   #I need to specify this is what is being included in write up

  #Adds in Quantiles based on the LADs we have data for
  prices <- prices %>%
    mutate(CountryClass = cut(X2, 
                              X2 %>% .[LAD11CD %in% unique(DATAdf$LAD11CD)] %>% quantile(.) %>%
                                .[2:4] %>% c(0,., Inf), 
                              labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
                              right = F) %>% fct_relevel(., "Upper", after = 3))

@@

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapQuartiles")
BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501)
BootStrapQuartiles <- LoadBootstrapData()

@@

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
BootstrapAllData(DATAdf, LimitValue = 2e5, Reps = 501, GroupingVars = "MSOA11CD")

BootStrapMSOA <- LoadBootstrapData()

@@

```{r}
CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
  df %>% 
  group_by(ID, Class) %>%
  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
  group_by(ID)%>%
  mutate(RatioExvsAct = LowUse/sum(LowUse)) %>%
  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1) %>%
    ungroup
}

test1 <- system.time(result <-  StrappedLowMem(dfPrice, dfWard, samples, Grouping = GroupVars))
test2 <- system.time(result <-  StrappedHighMem(dfPrice, dfWard, samples, Grouping = GroupVars))

LADS<-DATAdf%>%
  group_by(LAD11CD) %>%
  summarise(LAD11NM = first(LAD11NM)) %>%
  arrange(LAD11NM)

@@

test <- BootStrapQuartiles$E09000020

test <-DistribCompareBootstrapper(DATAdf%>%filter(LAD11CD == "E09000020"), samples = 100)

test2 <- test %>% 
  mutate(LowUse = Homes) %>%
  CleanForPlotClassDiff()

test3 <-test%>%
  group_by(ID)%>%
  mutate(RatioExvsAct = Homes/sum(Homes)) %>%
  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1) %>%
    ungroup

test2 %>% PlotClassDiff()

CleanForPlotClassDiff(BootStrapQuartiles$E09000020)  %>%
  PlotClassDiff(., "Kensington and Chelsea")
SaveFig("ClassdiffChelsea.pdf")

@@

#Plot for all data
All_data_class <- BootStrapQuartiles %>% 
  bind_rows %>%
  select(CountryClass, ID, LowUse, Homes) %>%
  rename(class = CountryClass) %>%
  CleanForPlotClassDiff

BootStrapQuartiles %>% 
  bind_rows %>%
  select(CountryClass, ID, LowUse, Homes) %>%
  rename(class = CountryClass) %>%
  #mutate(LowUse = Homes) %>%
  CleanForPlotClassDiff %>% 
  group_by(class) %>%
  summarise_all(mean)
